Topic Modeling of News

### 2017-10-25 paper/R/webhoseio_preprare2.Rmd

```{r}
rm(list =ls())

load("../output/news_cleaned.Rda")
```

@@

```{r}
pat <- 'Hinweis.+?(?=(einfügen))'
btw %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```
```{r}
as.data.frame(str_match(btw$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

  # Tagesschau
  x = gsub('Hinweis.+?(?=(einfügen))', "", x, perl = TRUE)

@@

# apply function to dataframe
df$text_cleaned <- clean.text(df$text)
```

```{r}
df$text_cleaned <- gsub("[[:punct:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:cntrl:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:digit:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("^[[:space:]]+", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:space:]]+$", " ", df$text_cleaned)
df$text_cleaned <- tolower(df$text_cleaned)
```

>>>>

```{r}
load("../output/news_cleaned.Rda")
```

@@

```{r}
pat <- 'ejf[^"]*'
df %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```
```{r}
as.data.frame(str_match(df$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

@@

# apply function to the "orig" dataframe
df$text_cleaned <- clean.text(df$text)
```

```{r}
preprocess.text <- function(x) {
  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space
  x = gsub("[[:cntrl:]]", " ", x)  # replace control characters with space
  x = gsub("[[:digit:]]", "", x)  # remove numbers
  x = gsub("^[[:space:]]+", "", x) # remove whitespace at beginning of documents
  x = gsub("[[:space:]]+$", "", x) # remove whitespace at end of documents 
  x = tolower(x)
  return(x)
}

# apply function to the "orig" dataframe
df$text_cleaned <- clean.text(df$text_cleaned)
```
